Simple Type Theory is not too Simple

### 2021-04-09 article.tex
Updates from Overleaf

	A more salient issue is the overall use of dependent types for defining some notions. For instance, [\dots] rewriting an expression such as $(f+~g)'(x)$ into $f'(x)+g'(x)$, while straightforward in mathematics, is next to impossible to achieve in Coq, as the proof terms have to be manually built by the user beforehand. Third, these proof terms can quickly blow up, and thus become impossible for the user to exhibit, \textit{e.g.} in the case of iterated derivatives or differentiation under an integral. By the way, integrals in Coq suffer from the same issues. \cite[1.]{boldo2015coquelicot}

@@

Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).  \\
Anthony Bordg thanks Kevin Buzzard for his stimulating wit and his communicative energy.

>>>>

	A more salient issue is the overall use of dependent types for defining some notions. For instance, [\dots] rewriting an expression such as $(f+~g)'(x)$ into $f'(x)+g'(x)$, while straightforward in mathematics, is next to impossible to achieve in Coq, as the proof terms have to be manually built by the user beforehand. Third, these proof terms can quickly blow up, and thus become impossible for the user to exhibit, \textit{e.g.}\ in the case of iterated derivatives or differentiation under an integral. By the way, integrals in Coq suffer from the same issues. \cite[p.\ts42]{boldo2015coquelicot}

@@

Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).  \\
We thank Kevin Buzzard for his stimulating wit and his communicative energy.
